Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/appendix.tex
moving code to appendix

\section{TraversableOnce Trait from Scala Standard Library}

\section{Proofs}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}.

>>>>

\section*{Appendix}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca} and the code discussed in Section~\ref{sec:collex}.

### 2015-03-08 sas2015/content/example.tex
moving and resizing figures
moving code to appendix

\subsection{An Example from the Scala Collections Library}
The Scala collections library contains the trait \code{TraversableOnce} that is
shared by both collections and iterators over them. 
%\ftodo{
%  I think it would be helpful to show a little more of the code of the trait here,
%  such as the trait declaration and the signature of the toArray method containing the
%  correlated calls. You can abbreviate everything else with ...
%}
The \code{toArray} method of this trait
creates an array and copies the contents of the collection or iterator into it:
\inputMintedNoLNs{scala}{collectionsExample.scala}
%\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
When \code{this} refers to an iterator rather than a collection, the call to \code{this.size}
extracts all elements of the iterator to count them.
%\ftodo{
%  Would it make sense to show the code for the size method, and refer to the line numbers
%  of that method in the above sentence?  
%}
 At the call to \code{copyToArray},
the iterator is already empty, so nothing is copied to the newly created array.
%\ftodo{
%Would it make sense to show the code for copyToArray here?
%}
One could design an IFDS analysis to detect this kind of bug.

@@

The relevant code from \textsf{TraversableOnce} and other related traits is shown
in Figure~\ref{fig:traversableonce}.

\begin{figure}
\inputMinted{scala}{TraversableOnce.scala}
\caption{Relevant code from \textsf{TraversableOnce} and related traits.}
\label{fig:traversableonce}
\end{figure}

>>>>

\subsection{An Example from the Scala Collections Library}\label{sec:collex}
The Scala collections library contains the trait \code{TraversableOnce} that is
shared by both collections and iterators over them. 
%\ftodo{
%  I think it would be helpful to show a little more of the code of the trait here,
%  such as the trait declaration and the signature of the toArray method containing the
%  correlated calls. You can abbreviate everything else with ...
%}
The \code{toArray} method of this trait
creates an array and copies the contents of the collection or iterator into it:
\inputMintedNoLNs{scala}{collectionsExample.scala}
%\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
When \code{this} refers to an iterator rather than a collection, the call to \code{this.size}
extracts all elements of the iterator to count them.
%\ftodo{
%  Would it make sense to show the code for the size method, and refer to the line numbers
%  of that method in the above sentence?  
%}
 At the call to \code{copyToArray},
the iterator is already empty, so nothing is copied to the newly created array.
%\ftodo{
%Would it make sense to show the code for copyToArray here?
%}
One could design an IFDS analysis to detect this kind of bug.

@@

The relevant code from \textsf{TraversableOnce} and other related traits is shown
in Figure~\ref{fig:traversableonce} in the Appendix.
